Universal regime transition for water resources utilization in developing river basins

### 2020-10-03 tex/main/manuscript.tex
update dilemmas and future directions

\section*{Dilemmas and future directions}
% 对于可持续科学，认识这种稳态的变化很重要
For sustainability scientists, recognizing that different regimes of water utilization regarding different water utilization regimes has important implications for social development and river basin management.
% 不同的流域位于过渡的不同阶段，面临的问题也存在区别，主要包括资源陷阱和结构陷阱两类。
At different transition phases, however, basins may face to various development dilemmas in water utilization, leading an unsustainable trajectory. 
% 资源陷阱和失配，导致崩溃
Like social-ecological systems and other complex systems, coupled human-water system may collapse under the stresses reached the tipping point or structural mismatches 
\cite{reyersSocialEcologicalSystemsInsights2018,cummingQuantifyingSocialEcologicalScale2020,wangCOSUSTMs0530Review}. 
% 转型应对陷阱
A number of studies have identified transformation as an important way out of unsustainable trajectory, and different types of transformation are required according to dominating regimes and dilemmas of \cite{scoonesTransformationsSustainabilityCombining2020a,steffenTrajectoriesEarthSystem2018}. 
% 我们的框架有助于理解和识别
Since our transition framework can identify regime shifts of water utilization, it may help to predict possible dilemmas in development.

% TODO 这里把图改成全球大河流域的资源问题类型图
\begin{figure}%[htbp]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main/big_rivers.pdf}
	\caption{
		\textbf{The Human Development Index of the world's great river basins, and the major problems facing some basins.}
		Overdependence on water resources for economic development in some basins, and high levels of human modification in others that have disrupted ecosystem structure. Data resources: Human Development Index in each basin refers from \cite{linkeGlobalHydroenvironmentalSubbasin2019}, strongly intervened basins and resource-dependent basins are come from Transboundary River Basins report by United Nations Environment Programme \url{http://geftwap.org/publications/river-basins-technical-report} \cite{unep-dhiTransboundaryRiverBasins2016}.
	}
	\label{fig:traps}
\end{figure}

% 世界各大流域面临的问题。资源开发早期容易陷入资源陷阱；流域发展后期容易陷入结构陷阱。
According to case studies around the world, big river basins often face resource dilemmas after resources-dependent developments, while highly developed ones need to resolve structural problems more often (Figure~\ref{fig:traps}).
% 黄河流域的发展过程，资源开发P2阶段陷入了资源陷阱（表现形式 xxx）。
In the Yellow River Basin, after the successive exploitation of agriculture (from P1 to P2, refers from natural cycle to a local cycle), industry and services, the water resource extraction rate has reached $79\%$, far exceeding the internationally recognized warning threshold of $40\%$. The resource dilemma revealed after the regime shift, with severe runoff outages and groundwater depletion of the Yellow River (\textit{SI Appendix} Fig. S8).
% 后来摆脱了资源陷阱（表现形式 xxx）。
To get rid of the resource dilemma, a clear transformation towards integrated basin management proposed, with several management practices (\textit{SI Appendix} Methods S5). These integrated management practices made the utilization of water resources into a regime of unified scheduling since the P3 in the Yellow River Basin, to escape from the “resource dilemma”.

% 一段有关87分水方案的介绍
The most important of these is the “87 Water Allocation Scheme”, which adopts a top-down approach in allocating water resources to all regions and sectors \cite{wangThirtyYearsYellow2018}. Since then, the scheme has been revised and refined, and a comprehensive water resources utilization system has gradually been formed that takes the basin scale into account \cite{wangThirtyYearsYellow2018}.

% 资源困局可能普遍存在
Since similar phenomena occurred in Mississippi and Indus River Basins, the fact that the accelerated development has been followed by water scarcity and a series of ecological problems shows that the resource dilemmas is pervasive in the transition trajectory, especially from natural cycle to regional cycle 
\cite{bestAnthropogenicStressesWorld2019,cummingResilienceBigRiver2011}.
% 结构困局可能普遍存在
Similarly, many of the world's major river basins have eventually moved towards a system of integrated governance, especially for trans-boundary rivers (e.g. Danube and Mekong River), where water resources are in need of collaborative governance \cite{bodinCollaborativeEnvironmentalGovernance2017}.

% 展望：未来还可能陷入结构陷阱，（表现形式：用水效率悖论的同时，倾向性停滞，灵活性进一步降低，）
However, basins still face structural dilemmas and require further transformation according to changes within the regional cycle of water utilization. 
Firstly, in line with paradox of irrigation efficiency, significant improvement in agricultural irrigation efficiency (i.e. decline in water use intensity) has been accompanied by a resurgence in irrigated area, resulting in an unabated and weak upward trend in water stress \cite{graftonParadoxIrrigationEfficiency2018}.
% 水资源压力仍在增大，而节水能力已经进入瓶颈，倾向性贡献减少）
Secondly, the changing priority between non-provisioning (i.e. industry and urban services) and provisioning (i.e. domestic and irrigation water use) is stagnating (see Figure~\ref{fig:dimensions}E) because of rigidify in the industrial structure. 
At the same time, the flexibility of water use is declining since domestic water use and thermal water use growth rapidly (supplementary Fig. S4). 
% 下一步：可以通过统一调控，调整格局来调整结构，突破结构陷阱。
% 总结：整个流域需进一步转型与适应，以实现高质量发展。
Typically, these may lead to a reduction in resilience of basins and leave highly coupled human-water systems facing greater vulnerability to collapse --as a structural dilemma \cite{cummingResilienceBigRiver2011}. Therefore, based on the identification of current phases and development dilemmas by the transition framework, further transformative governance is still needed to achieve a high-quality sustainable development of the basin \cite{scoonesTransformationsSustainabilityCombining2020a}.

>>>>

\section*{Dilemmas and future directions}
% 对于可持续科学，认识这种稳态的变化很重要
For sustainability scientists, recognizing that different regimes of water utilization regarding different water utilization regimes has important implications for social development and river basin management.
% 不同的流域位于过渡的不同阶段，面临的问题也存在区别，主要包括资源陷阱和结构陷阱两类。
At different transition phases, however, basins may face to various development dilemmas in water utilization, leading an unsustainable trajectory. 
% 资源陷阱和失配，导致崩溃
Like social-ecological systems and other complex systems, coupled human-water system may collapse under the stresses reached the tipping point or structural mismatches 
\cite{reyersSocialEcologicalSystemsInsights2018,cummingQuantifyingSocialEcologicalScale2020,wangCOSUSTMs0530Review}. 
% 转型应对陷阱
A number of studies have identified transformation as an important way out of these unsustainable trajectories, and different types of transformation are required according to dominating regimes and dilemmas of \cite{scoonesTransformationsSustainabilityCombining2020a,steffenTrajectoriesEarthSystem2018}. 
% 我们的框架有助于理解和识别
Since our transition framework can identify regime shifts of water utilization, it helps to predict possible dilemmas in development.

% TODO 这里把图改成全球大河流域的资源问题类型图
\begin{figure}%[htbp]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main/map.pdf}
	\caption{
		\textbf{The Human Development Index of the world's great river basins, and the major problems facing some basins.}
		Overdependence on water resources for economic development in some basins, and high levels of human modification in others that have disrupted ecosystem structure. Data resources: Human Development Index in each basin refers from \cite{linkeGlobalHydroenvironmentalSubbasin2019}, strongly intervened basins and resource-dependent basins are come from Transboundary River Basins report by United Nations Environment Programme \url{http://geftwap.org/publications/river-basins-technical-report} \cite{unep-dhiTransboundaryRiverBasins2016}.
	}
	\label{fig:traps}
\end{figure}

% 世界各大流域面临的问题。资源开发早期容易陷入资源陷阱；流域发展后期容易陷入结构陷阱。
According to cases all around the world, big river basins often face resource dilemmas after resources-dependent developments, while highly developed ones need to resolve structural problems more often (Figure~\ref{fig:traps}).
% 黄河流域的发展过程，资源开发P2阶段陷入了资源陷阱（表现形式 xxx）。
In the YRB as an example, after the successive exploitation of agriculture (from P1 to P2, refers from natural cycle to a local cycle), industry and services, the water resource extraction rate has reached $79\%$, far exceeding the internationally recognized warning threshold of $40\%$. The resource dilemma revealed after the regime shift, with severe runoff outages and groundwater depletion of the Yellow River (\textit{SI Appendix} Fig. S8).
% 后来摆脱了资源陷阱（表现形式 xxx）。
To get rid of the resource dilemma, a clear transformation towards integrated basin management proposed, with several management practices. 
% 一段有关87分水方案的介绍
The most important of these is the “87 Water Allocation Scheme”, which adopts a top-down approach in allocating water resources to all regions and sectors \cite{wangThirtyYearsYellow2018}. Since then, the scheme has been revised and refined, and a comprehensive water resources utilization system has gradually been formed that takes the basin scale into account \cite{wangThirtyYearsYellow2018}. 
These integrated management practices made the utilization of water resources into a regime of unified scheduling since the P3 in the Yellow River Basin, to escape from the resource dilemma. 
% 资源困局可能普遍存在
Since similar phenomena occurred in Mississippi and Indus River Basins, the fact that the accelerated development has been followed by water scarcity and a series of ecological problems shows that the resource dilemmas is pervasive in the transition trajectory, especially from natural cycle to regional cycle 
\cite{bestAnthropogenicStressesWorld2019,cummingResilienceBigRiver2011}.
% 通过协同治理来摆脱困局也普遍存在
Similarly, many of the world's major river basins have eventually moved towards a system of integrated governance, especially for trans-boundary rivers (e.g. Danube and Mekong River), where water resources are in need of collaborative governance \cite{bodinCollaborativeEnvironmentalGovernance2017,unep-dhiTransboundaryRiverBasins2016}.

% 此外，即使发展极大提升了用水效率，黄河流域的困境也并没能完全解决。
In addition, further dilemmas of the YRB has not been completely solved though water use efficiency greatly improved by development.
% 展望：未来还可能陷入结构陷阱，（表现形式：用水效率悖论的同时，倾向性停滞，灵活性进一步降低，）
% Therefore, basins still in need of further transformations according to changes within the transition cycle of water utilization. 
Firstly, in line with paradox of irrigation efficiency, significant improvement in agricultural irrigation efficiency has been accompanied by re-growths in irrigated area, still resulting in an unabated and weak upward trend in water resources stress \cite{graftonParadoxIrrigationEfficiency2018}.
% 水资源压力仍在增大，而节水能力已经进入瓶颈，倾向性贡献减少）
Secondly, the changing priority between non-provisioning (i.e. industry or services) and provisioning (i.e. domestic and irrigation water use) may rigidify the flexibility of water use, since domestic water use and thermal water use growth rapidly (supplementary Fig. S4). 
% 下一步：可以通过统一调控，调整格局来调整结构，突破结构陷阱。
% 总结：整个流域需进一步转型与适应，以实现高质量发展。
Typically, these may lead to a reduction in resilience of basins and leave highly coupled human-water systems facing greater vulnerability to collapse --as a structural dilemma \cite{cummingResilienceBigRiver2011}. Therefore, based on the identification of current phases and development dilemmas by the transition framework, further transformative governance is still needed to achieve a high-quality sustainable development of the basin, because development is not a panacea for the dilemmas \cite{scoonesTransformationsSustainabilityCombining2020a}.
